Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-27 manuscript.Rmd
Fix references and update replies call

Following a wave of democratization efforts across the Middle East and North
Africa, modest Syrian protests began in March 2011. The regime responded harshly
with imprisonments, detentions, censorship, and military operations as the
resistance to Assad's regime spread. The fighting escalated dramatically in
March 2012, after increased unrest in the western city of Homs. International
actors---including the Red Cross/Red Crescent Society, the United Nations
General Assembly, the U.N. Security Council, and individual world
leaders---worked toward cease-fires, negotiations, and concessions without much
success. While many high-level military and diplomatic officials defected,
numerous loyal forces continued the regime's repression, and the Syrian people
turned to social media to coordinate their activism and communicate to the
world. Between March and June 2012, millions of tweets were sent within
Syria, revealing the details of the conflict suppressed by the government. A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016ne].

@@

The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets and `r tweet_stats$percent_retweets_all`% retweets. There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.

@@

# detach plyr so summarise works
detach("package:plyr", unload=TRUE)

>>>>

Following a wave of democratization efforts across the Middle East and North
Africa, modest Syrian protests began in March 2011. The regime responded harshly
with imprisonments, detentions, censorship, and military operations as the
resistance to Assad's regime spread. The fighting escalated dramatically in
March 2012, after increased unrest in the western city of Homs. International
actors---including the Red Cross/Red Crescent Society, the United Nations
General Assembly, the U.N. Security Council, and individual world
leaders---worked toward cease-fires, negotiations, and concessions without much
success. While many high-level military and diplomatic officials defected,
numerous loyal forces continued the regime's repression, and the Syrian people
turned to social media to coordinate their activism and communicate to the
world. Between March and June 2012, millions of tweets were sent within
Syria, revealing the details of the conflict suppressed by the government. A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016new].

@@

The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets, `r tweet_stats$percent_retweets`% retweets, and `r tweet_stats$percent_replies`% replies. There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.

@@

# detach plyr so summarise works
#detach("package:plyr", unload=TRUE)
